### 2015-11-05 docs/references.tex
Issue 1405: added new docs directory with content
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2764 40876441-3496-0410-a613-a2fca35b2ae2
Additional notes on addressing model
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2765 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  references.tex
%
%  Bibliography
%
%  $Id$
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2011 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\bibitem{cpc}
Desplat, J.-C., I. Pagonabarraga, and P. Bladon,
LUDWIG: A parallel lattice-Boltzmann code for complex fluids.
\textit{Comput. Phys. Comms.}, \textbf{134}, 273, 2001.

@@

@@

\bibitem{ieee-208}
IEEE Standard 208-2005, IEEE Standard for Software Configuration Management
Plans. See \texttt{http://ieeexplore.ieee.org/xpl/standards.jsp}
(accessed 2011).

@@

\bibitem{viv}
Kendon, V.M., M.E. Cates, I. Pagonabarraga, J.-C. Desplat, and
P. Bladon,
Inertial effects in three dimensional spinodal decomposition of
a symmetric binary fluid mixture: A lattice Boltzmann study,
\textit{J. Fluid Mech.}, \textbf{440}, 147 (2001).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  references.tex
%
%  Bibliography
%
%  $Id: references.tex 1902 2013-01-31 15:11:10Z ohenrich $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2011 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\bibitem{apacheAPR} 
Apache Portable Runtime Project ``APR's Version Numbering''.
See, e.g., \texttt{https://apr.apache.org/versioning.html)}
(accessed November 2015).

@@

\bibitem{desplat2001}
Desplat, J.-C., I. Pagonabarraga, and P. Bladon,
LUDWIG: A parallel lattice-Boltzmann code for complex fluids.
\textit{Comput. Phys. Comms.}, \textbf{134}, 273, 2001.

@@

\bibitem{gray2013}
A. Gray and K. Stratford,
TargetDP reference.

@@

\bibitem{ieee-208}
IEEE Standard 208-2005, IEEE Standard for Software Configuration Management
Plans.
See \texttt{http://ieeexplore.ieee.org/xpl/standards.jsp}
(accessed November 2015).

\bibitem{ieee-828-2012}
IEEE Standard 828-2012. IEEE Standard for Configuration
Management in Systems and Software Engineering. 
See \texttt{http://ieeexplore.ieee.org/xpl/standards.jsp}
(accessed November 2015).

@@

\bibitem{kendon2001}
Kendon, V.M., M.E. Cates, I. Pagonabarraga, J.-C. Desplat, and
P. Bladon,
Inertial effects in three dimensional spinodal decomposition of
a symmetric binary fluid mixture: A lattice Boltzmann study,
\textit{J. Fluid Mech.}, \textbf{440}, 147 (2001).
